---
title: "Data Analyses"
author: "Kaleem Ullah"
date: "2024-04-22"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir="/courses/RA - Spring 2024/Gorilla Data")
knitr::opts_knit$set(root.dir="D://RA - Spring 2024//Gorilla Data")
require(tidyverse)
require(lme4)
require(ggplot2)
require(brms)
library(dplyr)
```

# Exploratory Data Analyses

```{r explore}
df <- read.csv("new_csv//preprocessed_data.csv")
length(unique(df$ppn))
```

## Preliminary Analyses

```{r}
df$culture <- as.factor(df$culture)
df$ppn2 <- as.factor(df$ppn2)
df$emotion <- as.factor(df$emotion)
df$accuracy <- as.factor(df$accuracy)

# Define control settings for the optimizer
control_settings <- glmerControl(optimizer = "bobyqa",
                                 optCtrl = list(maxfun = 1e5),  # increase max function evaluations
                                 calc.derivs = TRUE,
                                 check.conv.grad = .makeCC("warning", tol = 1e-3, relTol = NULL))


# Hypothesis 1
accuracy_fit_1 <- glmer(accuracy ~ culture + (1 | emotion), 
                      data = df, 
                      family = binomial,
                      control = control_settings)

# accuracy_fit_2 <- glmer(accuracy ~ culture + (1 | ppn2/emotion), 
#                       data = df, 
#                       family = binomial, 
#                       control = control_settings)
# 

summary(accuracy_fit_1)
# summary(accuracy_fit_2)
anova(accuracy_fit_1) # , accuracy_fit_2)
```
```{r}
help(isSingular)
```



## Effects size: Odds Ratio

Odds Ratio (OR): An odds ratio greater than 1 indicates that the odds of the event (e.g., success) are higher for higher values of the predictor, while an odds ratio less than 1 indicates lower odds.

```{r}
# Chinese 
coefs <- fixef(accuracy_fit_1)
coef_CN <- coefs["cultureCN"]
odds_ratio_1 <- exp(coef_CN)
print(odds_ratio_1)

# Dutch
coefs <- fixef(accuracy_fit_1)
coef_NL <- coefs["cultureNL"]
odds_ratio_2 <- exp(coef_NL)
print(odds_ratio_2)

# Adoptee
coefs <- fixef(accuracy_fit_1)
coef_AD <- coefs["Intercept"]
odds_ratio_3 <- exp(coef_AD)
print(odds_ratio_3)


```



# Likert 1 

```{r}
# Hypothesis 2
iden_fit <- lmerTest::lmer(likert1 ~ culture + (1 | ppn),
                 data=df)
# summary(iden_fit)
summary(iden_fit)
```

```{r}
ggplot(df, aes(x = likert1, y = culture)) + geom_violin() + labs(title = "Distribution of Likert1 by Culture")
```

## Effect Size: Cohen's d

Cohen's d: Cohen's d represents the effect size in standard deviation units. 

A value of d=0.2 is considered a small effect, d=0.5 a medium effect, and d=0.8 a large effect.

```{r}
# Chinese
lmer_coef <- fixef(iden_fit)
lmer_CN <- lmer_coef["cultureCN"]
lmer_d <- lmer_CN / sd(na.omit(df$likert1))
print(lmer_d)

# Dutch
lmer_coef <- fixef(iden_fit)
lmer_NL <- lmer_coef["cultureNL"]
lmer_d <- lmer_NL / sd(na.omit(df$likert1))
print(lmer_d)
```


# Likert 2

```{r}
iden_fit_2 <- lmerTest::lmer(likert2 ~ culture + (1 | ppn),
                 data=df)
summary(iden_fit_2)
# anova(iden)
```

```{r}
# Chinese
lmer_coef <- fixef(iden_fit_2)
lmer_CN <- lmer_coef["cultureCN"]
lmer_d <- lmer_CN / sd(na.omit(df$likert2))
print(lmer_d)

# Dutch
lmer_coef <- fixef(iden_fit_2)
lmer_NL <- lmer_coef["cultureNL"]
lmer_d <- lmer_NL / sd(na.omit(df$likert2))
print(lmer_d)
```


```{r}
ggplot(df, aes(x = culture, y = likert2)) + geom_violin() + labs(title = "Distribution of Likert2 by Culture")
```

## Bayesian Analyses for Hypothesis 2

Compare where dutch and 
```{r}
# Model 1
priors_CN <- set_prior("normal(5, 2)", class = "b", coef = "cultureCN")
priors_NL <- set_prior("normal(3, 2)", class = "b", coef = "cultureNL")
priors_AD <- set_prior("normal(5, 2)", class = "Intercept")

# Model 2
priors_CN <- set_prior("normal(5, 2)", class = "b", coef = "cultureCN")
priors_NL <- set_prior("normal(3, 2)", class = "b", coef = "cultureNL")
priors_AD <- set_prior("normal(3, 2)", class = "Intercept")


df = na.omit(df)

bayesian_model <- brm(likert1 ~ culture + (1 | ppn), data = df, prior = c(priors_CN,priors_NL, priors_AD))
summary(bayesian_model)



```
```{r}
bayesian_model$
```


```{r}
priors_CN <- set_prior("uniform(0, 10)", class = "b", coef = "cultureCN")
priors_NL <- set_prior("uniform(0, 10)", class = "b", coef = "cultureNL")
priors_AD <- set_prior("uniform(0, 10)", class = "Intercept")

df = na.omit(df)

bayesian_model <- brm(likert1 ~ culture + (1 | ppn), data = df, prior = c(priors_CN,priors_NL, priors_AD))
summary(bayesian_model)
```


## Interpretation
 A negative intercept indicates that the log-odds of the outcome occurring (e.g., success, presence, yes) is less than zero when all predictors are zero, which translates to a probability less than 0.5. This means that the base level of the outcome is more likely not to occur than to occur at the baseline level of the predictors.

```{r}
# df = na.omit(df)

# Hypothesis 3
glm_fit <- glmer(accuracy ~ culture + likert1 + (1 | emotion),
                 data = df, 
                 family = binomial, 
                 control = glmerControl(optimizer = "bobyqa"),
                 nAGQ = 10)

glm_fit_2 <- glmer(accuracy ~ culture + likert2 + (1 | emotion),
                 data = df, 
                 family = binomial)


summary(glm_fit)
summary(glm_fit_2)
```



# Demographics

```{r}
demo_data <- read.csv("new_csv/prelim_demo.csv", header=T)
```

```{r}
ratio <- sum(demo_data$gender == '男') / sum(demo_data$gender == '女')
```

Mean Age: `r mean(demo_data$age)` 
Ratio of Male/Female: `r ratio`


