---
title: "Preliminary Data Screening"
author: "Kaleem Ullah"
date: "2024-03-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir="/courses/RA - Spring 2024/Gorilla Data")
require(tidyverse)
```

## Check the percentage of videos that were played

```{r}
# setwd('D:\\RA - Spring 2024\\Gorilla Data\\raw_data')
video_data_recog <- read.csv("metadata/recog_flat.csv", header=TRUE)
video_data_iden <- read.csv("metadata/iden_flat.csv", header=TRUE)
video_data_recog['trial'] = video_data_recog['trial.number']
video_data_iden['trial'] = video_data_iden['trial.number']

num_ppn_recog <- length(unique(video_data_recog$ppn))
num_ppn_iden <- length(unique(video_data_iden$ppn))
df_recog <- read.csv("raw_data/emotion_recog.csv", header=TRUE)
df_iden <- read.csv("raw_data/emotion_iden.csv", header=TRUE)
expected_played_recog <- num_ppn_recog*24
expected_played_iden <- num_ppn_iden*24
videos_played_recog <- length(video_data_recog$reaction.recog)
videos_played_iden <- length(video_data_iden$reaction.iden)
```


```{r}
head(video_data_recog)
```


## Check individually for each task


Expected videos played: `r expected_played_recog` 

Total videos played: `r videos_played_recog` 

Percentage of videos played: `r videos_played_recog/expected_played_recog*100` 


### 1. Recognition Task

**Videos Played**

```{r}
zoneType <- df_recog$Zone.Type
last_iter = "response_button_text"
unplayed = 0
for (i in zoneType){
  if (last_iter == "response_button_text" & i  == "response_button_text") {
    unplayed = unplayed + 1
  }
  last_iter = i
}
unplayed / length(df_recog$Zone.Type)
```

**Reaction Time**

```{r}
reac_recog <- sum(video_data_recog$reaction.recog < 1000, na.rm=TRUE)
```

Percentage of videos played less than 1 second: `r reac_recog/videos_played_recog * 100`

## Time Taken for each task

```{r}
total_time_recog <- as.numeric(df_recog[df_recog$Trial.Number == "END TASK",]$Reaction.Time) / 1000
```

```{r}
summary(total_time_recog)
```


### 2. Identification Task

Expected videos played: `r expected_played_iden`

Total videos played: `r videos_played_iden`

Percentage of videos played: `r videos_played_iden/expected_played_iden*100`

```{r}
reac_iden <- sum(video_data_iden$reaction.iden < 1000, na.rm=TRUE)
```

Percentage of videos played less than 1 second: `r reac_iden/videos_played_recog * 100`


```{r}
total_time_iden <- as.numeric(df_iden[df_iden$Trial.Number == "END TASK",]$Reaction.Time) / 1000
```

```{r}
summary(total_time_iden)
```


## Percentage of videos watched by participants

# Recognition

## Check number of videos played

```{r}
num_ppn <- length(unique(video_data_recog$CINT))
# cint_id <- length(unique(video_data_recog$ppn))
number_per_ppn <- numeric(num_ppn)
ppns <- as.list(unique(video_data_recog['CINT']))
cint_id_list <- as.list(unique(video_data_recog['CINT']))


i = 0
for (each_ppn in ppns$CINT) {
  # print(each_ppn)
  # print()
  number_per_ppn[i] <- length(video_data_recog$trial[video_data_recog["CINT"] == each_ppn])
  # print(numbers_per_ppn)
  i = i + 1
}
```

# Create csv with number of videos watched

```{r}
videos_per_ppn1 <- data.frame(ppn = ppns, videos = number_per_ppn)
write.csv(videos_per_ppn1, 'metadata/videos_per_ppn_1.csv')
```


```{r}
ratio_vids <- numeric(23)
for (i in 1:24) {
  # print(i)
  ratio_vids[i] <- sum(number_per_ppn < i) / num_ppn
}
```

```{r}
# png("plots/ratio_recog.png", width=800, height=600)
plot(ratio_vids[1:20], main = "The Ratio of Unwatched Videos at Participant Level (Block 1)", ylab="Ratio of participants", xlab="Number of Videos")
# dev.off()
```


```{r}
print(sum(number_per_ppn < 12) / num_ppn)
```


### Identification


```{r}
num_ppn <- length(unique(video_data_iden$CINT))
number_per_ppn <- numeric(num_ppn)
ppns <- as.list(unique(video_data_iden['CINT']))
# cint_id_list2 <- as.list(unique(video_data_recog['CINT']))
i = 0
for (each_ppn in ppns$CINT) {
  # print(each_ppn)
  # print()
  number_per_ppn[i] <- length(video_data_iden$trial[video_data_iden["CINT"] == each_ppn])
  # print(numbers_per_ppn)
  i = i + 1
}
```


```{r}
videos_per_ppn2 <- data.frame(ppn = ppns, videos = number_per_ppn)
write.csv(videos_per_ppn2, 'metadata/videos_per_ppn_2.csv')
```

```{r}
ratio_vids <- numeric(23)
for (i in 1:24) {
  # print(i)
  ratio_vids[i] <- sum(number_per_ppn < i) / num_ppn
}
```

```{r}
# png("plots/ratio_iden.png", width=800, height=600)
plot(ratio_vids[1:20], main = "The Ratio of Unwatched Videos at Participant Level (Block 2)", ylab="Ratio of participants", xlab="Number of Videos")
# dev.off()
```


```{r}
print(sum(number_per_ppn < 12) / num_ppn)
```


```{r}
for (i in 1:24) {
  # print(i)
  print(sum(number_per_ppn < i) / length(number_per_ppn))
}
```


## Accuracy Check in difference for reaction time

```{r}
less_than_one <- video_data_recog[video_data_recog$reaction.recog < 1000, ]
more_than_one <- video_data_recog[video_data_recog$reaction.recog > 1000, ]
```


```{r}
clean_data <- read.csv("new_csv/preprocessed_data.csv", header = TRUE)
```


```{r}
join_less <- clean_data %>% right_join(less_than_one, by=c("trial", 'ppn'), relationship = "many-to-many")
join_less <- na.omit(join_less)
sum(join_less$accuracy) / length(join_less$accuracy)
```

```{r}
join_more <- clean_data %>% right_join(more_than_one, by=c("trial", 'ppn'), relationship = "many-to-many")
join_more <- na.omit(join_more)
sum(join_more$accuracy) / length(join_more$accuracy)
```
